### 2015-06-26 abstract.tex
new outline changes

\noindent
Outline and writing assignments:
later the abstract will go here.
\begin{enumerate}
\item Introduction - Scott - Hasan - Gary - Jay 4 pages
   \begin{enumerate}
      \item resource drivers
      \item application drivers
      \item overall example which we will use for the test
      \item  need to answer the questions what we are doing, research  , prototype, aim, and what is new
   \end{enumerate}
\item Enabling Technologies - Jay - 1 page
   \begin{enumerate}
   	\item Sirocco
   	\item ADIOS
   	\item DataSpaces
   	\item Anything else
   \end{enumerate}
 \item {Proposed Research and Methods} - 14 pages
    \begin{enumerate}
       \item Application interface - Hasan, Manish, Gary, Kimmy, Jay, Mark
          \begin{enumerate}
            \item APIS - Kimmy  (rules/policy, user decision of data compression, quick feedback from system monitoring, QoS)
            \item description of data - Gary
            \item collection of data reduction techniques - Mark
            \item data re-organization specification - Scott, Mark
            \item QoS - Hasan
            \item data placement and movement (anticipatory and on-demand)  - Gary/Manish
            \item policies - Jay
          \end{enumerate}
      \item Storage System - Jay, Carlos, Manish, Lee, Matthew, Feyi
      \begin{enumerate}
         \item migration - Lee
         \item resource management -Jay
         \item QoS - Carlos 
         \item Discovery - Jay
         \item Eviction metrics - Carlos
         \item Naming Service (not completely sure what this is?) - Manish
         \item Estimation of Times - Feyi
      \end{enumerate}
    \end{enumerate}
\item Evaluation - 1 pages
\item Timetable of Activities - 1/2 page
\item Project Management Plan - 1 page
\item Project Objective  1/2 page
\end{enumerate}

>>>>

\noindent
Outline and writing assignments:
later the abstract will go here.
\begin{enumerate}
\item Introduction - Scott - Hasan - Gary - Jay 4 pages
   \begin{enumerate}
      \item resource drivers
      \item application drivers
      \item overall example which we will use for the test
      \item  need to answer the questions what we are doing, research  , prototype, aim, and what is new
   \end{enumerate}
\item Enabling Technologies - Jay - 1 page
   \begin{enumerate}
   	\item Sirocco
   	\item ADIOS
   	\item DataSpaces
   	\item Anything else
   \end{enumerate}
 \item {Proposed Research and Methods} - 14 pages
          Proposed work
          Execution path
          Related work

    \begin{enumerate}
       \item Application interface - Hasan, Manish, Gary, Kimmy, Jay, Mark
          \begin{enumerate}
            \item APIS - Kimmy  (rules/policy, user decision of data compression, quick feedback from system monitoring, QoS)
            \item description of data - Gary `` how we describe the structure and semantic of the data, how will it be stored, application level importance, utility curve''
            \item collection of data reduction techniques - Mark
            \item data re-organization specification - Scott, Mark
            \item QoS - Hasan/Gary/Carlos - emission control, some guarantees on the estimates
            \item data placement and movement (anticipatory and on-demand)  - Manish, Gary 
            \item policies - Jay
          \end{enumerate}
      \item Storage System - Jay, Carlos, Manish, Lee, Matthew, Feyi
      \begin{enumerate}
         \item migration - Lee
         \item Match organization of data with the medium characteristics - Carlos, Hasan
         \item Eviction metrics - Carlos, Hasan
         \item resource management -Jay
         \item QoS - Carlos 
         \item Discovery - Jay - moves things based on pressure on the system, getting to some things take effort because it is at different places, understand what our different options in terms of data quality... ability to decide the trade-offs 
         \item Naming Service (not completely sure what this is?) - Jay
          \item data placement and movement (anticipatory and on-demand) from a storage system perspective - Manish 
         \item Estimation of Times - Feyi
      \end{enumerate}
    \end{enumerate}
\item Evaluation - 1 pages - Scott
\item Timetable of Activities - 1/2 page
\item Project Management Plan - 1 page - Scott
\item Project Objective  1/2 page
\end{enumerate}
